Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-24 paper/paper.tex
#28 include controls table
Updates from Overleaf

Because the \textit{Städtebuch} data compiled by \cite{pt2} records exactly how each city was acquired by the territory holding it, I am able to estimate heterogeneous effects for different types of ownership changes.\footnote
{
Presumably \cite{schoenholzer2022}, having sourced their data on territorial histories from historical maps, lack detailed information about individual switching events. They instead use clever panel decomposition methods (pp. 14-20) and data on state-level characteristics (pp. 21-23) to explain what drives their estimates.
}
For this purpose I extend Equation \eqref{eq:sw22} by interacting the treatment indicator with the type of switching event:
\begin{equation}
\label{eq:baseline}
\begin{split}
    construction_{it} &= \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0)\beta +
    \mathbf{1}(t \ge e^{NewState}_i)\pi \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Conquest_{it}) \times \theta_{conquest} \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Other_{it}) \times \theta_{other} + \varepsilon_{it},
\end{split}
\end{equation}

For clarity I move from the event study to a basic difference-in-differences specification; this way there is only a single coefficient of interest. I simply replace the lead and lag dummies with the post-treatment indicator $\mathbf{1}(t \ge e^{NewState}_i)$. The more important novelty are the interaction terms: I interact the post-treatment indicator with the type of switch to obtain estimates of how the trends in construction activity differ after different types of switches. I distinguish three categories: $Conquest$, $Succession$, and $Other$. In all cases this refers to how the state currently owning the city came into power --- for example $Conquest_{it} = 1$ means that the state that holds city $i$ at time $t$ acquired city $i$ by conquest. It will be useful to adopt one final bit of notation from \cite{schoenholzer2022} and let $\mathbf{J}(i, t)$ denote the state ruling city $i$ at time $t$.

@@

@@

>>>>

Because the \textit{Städtebuch} data compiled by \cite{pt2} records exactly how each city was acquired by the territory holding it, I am able to estimate heterogeneous effects for different types of ownership changes.\footnote
{
Presumably \cite{schoenholzer2022}, having sourced their data on territorial histories from historical maps, lack detailed information about individual switching events. They instead use clever panel decomposition methods (pp. 14-20) and data on state-level characteristics (pp. 21-23) to explain what drives their estimates.
}
For this purpose I extend Equation \eqref{eq:sw22} by interacting the treatment indicator with the type of switching event:
\begin{equation}
\label{eq:baseline}
\begin{split}
    construction_{it} &= \alpha_i + \delta_t + \mathbf{X}_{it} \beta + 
    \mathbf{1}(t \ge e^{NewState}_i) \pi \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Conquest_{it}) \cdot \theta_{conquest} \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Other_{it}) \cdot \theta_{other} + \varepsilon_{it},
\end{split}
\end{equation}

For clarity I move from the event study to a basic difference-in-differences specification; this way there is only a single coefficient of interest. I simply replace the lead and lag dummies with the post-treatment indicator $\mathbf{1}(t \ge e^{NewState}_i)$. Also, this equation features a vector of city-year level control variables $\mathbf{X}_{it}$. In the baseline version of this specification I control only for the dummy $\mathbf{1}(S_{it} > 0)$ that indicates switches in the same period, exactly like in Equation \eqref{eq:sw22}. In a robustness check I will additionally control for conflict incidents.

The more important novelty are the interaction terms: I interact the post-treatment indicator with the type of switch to obtain estimates of how the trends in construction activity differ after different types of switches. I distinguish three categories: $Conquest$, $Succession$, and $Other$. In all cases this refers to how the state currently owning the city came into power --- for example $Conquest_{it} = 1$ means that the state that holds city $i$ at time $t$ acquired city $i$ by conquest. It will be useful to adopt one final bit of notation from \cite{schoenholzer2022} and let $\mathbf{J}(i, t)$ denote the state ruling city $i$ at time $t$.

@@

table 3: why neg? conflict NA may be systematocally correlated

are some regions more common in the conflict NAs?

The first explanation is that conflict is an important omitted variable, in the sense that it is correlated both with the treatment and with construction activity.

If omitting  bias in $\theta_{conflict}$ from omitting conflict has the same sign as 
$$\beta_{conflict} \cdot \frac{\mathbf{Cov}({Conflict},\: {Switching\: to\: another\: state \times Conquest})}{\mathbf{Var}(Conflict)}$$

The whole term is negative. We can see in Columns (3) and (4) of Table \ref{tab:controls_50y} that $\beta_{conflict}$ has a positive sign. It follows that the correlation between must be negative (which makes sense - an owner with higher state power is likely better able to protect a city from attacks.

But if $\beta_{conflict}$ is around zero, then why does it introduce bias at all?

It doesn't make sense. It has to be something about the sample. Johannes must have been spot on.

@@

\input{paper/output/regressions/controls_50y}
